\documentclass[12pt]{article}
\usepackage[top=0.9in, bottom=0.9in, left=0.9in, right=1.1in]{geometry}

\usepackage{graphicx,color,enumitem,fancyvrb,xspace}
\usepackage{amsmath,amsthm,amsbsy}
\usepackage{palatino}
\usepackage{mdframed}

\usepackage{tikz}
\usepackage[colorlinks=true,urlcolor={blue}]{hyperref}

\mdfdefinestyle{exerpartSty}{}
\theoremstyle{definition}
\newmdtheoremenv[style=exerpartSty,linewidth=0.5pt, topline=false, bottomline=false, rightline=false,%
leftmargin=0pt, innerleftmargin=0.4em, rightmargin=0pt, innerrightmargin=0pt, innertopmargin=-5pt ,%
innerbottommargin=3pt, splittopskip=\topskip, splitbottomskip=0.3\topskip, %
skipabove=1.3\topsep]{exerpart}{Part}

\renewcommand*{\theexerpart}{(\alph{exerpart})}
\newcommand{\eps}{\epsilon}
\newcommand{\Matlab}{\textsc{Matlab}\xspace}
\newcommand{\Octave}{\textsc{Octave}\xspace}

%% The following commands put defined left and right headers on the top, and a page number
%% on the bottom of all pages beyond page 1
\makeatletter
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot[C]{\ifnum \value{page} > 1\relax\thepage\fi}
\fancyhead[L]{\ifx\@doclabel\@empty\else\@doclabel\fi}
\fancyhead[R]{\ifx\@docdate\@empty\else\@docdate\fi}
\headheight 15pt
\def\doclabel#1{\gdef\@doclabel{#1}}
\def\docdate#1{\gdef\@docdate{#1}}
\makeatother

%% General formatting parameters
\parindent 0pt
\parskip 6pt plus 1pt

\newcommand{\epart}[1]{\noindent \textbf{(#1)} \,}

\doclabel{Math F302 UX1: Mini-Project 5}
\docdate{due \emph{at 11pm} on Monday 22 April 2019}

\begin{document}
\renewcommand{\d}{\displaystyle}

\strut
\centerline{{\Large \textsc{One problem, many methods}}}

\medskip
\centerline{{\large a review assignment}}

\medskip
\small
\renewcommand{\baselinestretch}{0.95}
\begin{quote}
\textbf{Instructions.}  Please write your solutions neatly on paper, or start a new document on a computer.  Include your name in the upper right on each sheet.  Clearly label the parts of your solutions following the headings below.    Your final document, which should \emph{not} be your first draft, should be at most five pages.  Please show your work neatly.  Full credit requires evidence of clear understanding \emph{and} clear writing.  If you wrote on paper, please scan or photograph your completed document and make the lighting good.  Also line things up carefully, and/or use a scanner app.  In any case \emph{please generate a single easily-readable PDF file.}  Then submit your PDF by uploading using the Google Form link on the ``Week 14'' page at

     \centerline{\href{https://bueler.github.io/math302/index.html}{\texttt{bueler.github.io/math302}}}  
\end{quote}

\normalsize
\bigskip
\renewcommand{\baselinestretch}{1.1}

Though many real-world ODEs are nonlinear, a large fraction of the problems this course, and on the Final Exam, are linear ODEs of second order.  This Mini-Project reviews our methods for such problems.  There is no new content.

Because of how this Mini-Project is structured, the final answer in each part, i.e.~the value of $x(2)$, is not worth many points!  What you need to do is show understanding and correct application of each method.

\medskip
\textbf{One problem}.  Consider this ODE IVP for an unknown function $x(t)$:
\begin{equation}
x''+4x'+5x=0, \quad x(0)=0, \, x'(0)=10 \label{homo}
\end{equation}
Parts A--E below ask you to use five different methods to compute, or approximate, $x(2)$.  Because this answer is the same in each case, you can check your work.

Also consider this closely-related non-homogeneous variation of the same problem:
\begin{equation}
x''+4x'+5x=5\sin t, \quad x(0)=0, \, x'(0)=10 \label{nonhomo}
\end{equation}
Parts G--I ask you to compute $x(2)$ for this problem using three different methods.

\medskip
\textbf{Many solution methods}.  The emphasis of your solutions must be on showing clear understanding of the steps of the method, and correctness also.  Please consistently write ``$x(t)$'' for the solution, that is, with independent variable $t$ and dependent variable $x$.

\renewcommand{\labelenumi}{\Alph{enumi}.}
\begin{enumerate}
\item Use \emph{auxiliary equation} methods from \S4.3 to solve problem \eqref{homo}.  Compute $x(2)$.
\item Use \emph{Laplace transform} methods from Chapter 7 to solve problem \eqref{homo}.  Compute $x(2)$.
\item In the \href{https://bueler.github.io/math302/assets/slides/5-3.pdf}{slides} and \href{https://expl.ai/VSJTFRC}{video} for \S5.3/4.10 I show how to use the \Matlab/\Octave black-box solver \href{https://www.mathworks.com/help/matlab/ref/ode45.html}{\texttt{ode45}} to solve second-order ODE IVPs like this one.  Use the substitution $z_1(t)=x(t)$ and $z_2(t)=x'(t)$ to write equation \eqref{homo} as a first-order system.  Then use \Matlab/\Octave/\href{https://octave-online.net/}{OctaveOnline} to solve the problem \emph{numerically}:
\begin{Verbatim}[fontsize=\small]
>> f = @(t,z) [_____; _____];
>> [tt,zz] = ode45(f,[0,2],[_____;_____]);
>> plot(tt,zz),  xlabel t,  legend('x(t)','dx/dt')
\end{Verbatim}
%> f = @(t,z) [z(2); -5*z(1)-4*z(2)];
%> [tt,zz]=ode45(f,[0,2],[0;10]);
%> plot(tt,zz),  xlabel t,  legend('x(t)','dx/dt')
%> zz(end,1)
%ans =  0.16654
%> abs(zz(end,1)-10*sin(2)/exp(4))
%ans =    5.6262e-06
You will need to fill in the blanks.  Thereby approximate $x(2)$.  How accurate is the approximation?  (\emph{Compute the absolute error; it is \emph{not} zero; \emph{\texttt{ode45}} is \emph{not} magic.})
\item Use the \emph{power series} methods from \S6.2 to solve problem \eqref{homo}.  In particular, start your solution with a power series around the basepoint $t_0=0$, namely
    $$x(t) = \sum_{n=0}^\infty c_n t^n.$$
Use known values $x(0)$ and $x'(0)$ to find $c_0$ and $c_1$.  Find the recurrence relation which generates all of the coefficients $c_n$.  Determine the values of $c_2,\dots,c_6$.  Now $x(t)$ is approximated by a polynomial of degree 6, i.e.~$x(t)\approx p(t)$.  What is the approximation of $x(2)$?  (\emph{It will not be close to the result from the other parts.})  Closer to the basepoint, what is the approximation of $x(1)$?  (\emph{This should be much better; compare the solution from parts A and/or B.})  On the same axes, plot both the exact solution $x(t)$---from parts A and/or B---and the polynomial $p(t)$ on $0\le t \le 2$.
\item Write equation \eqref{homo} as a first order system as in \S8.1.  That is, use the substitution $y(t)=x'(t)$, and find a $2\times 2$ matrix $\mathbf{A}$ and an initial vector $\mathbf{X}_0$, so that the problem is
    $$\mathbf{X}' = \mathbf{A} \mathbf{X}, \quad \mathbf{X}(0)=\mathbf{X}_0$$
for a vector solution $\mathbf{X}(t) = \begin{pmatrix} x(t) \\ y(t) \end{pmatrix}$.  The eigenvalues and eigenvectors of this system will be complex.  To avoid confusion, you may use the fact that eigenvalues and eigenvectors of $\mathbf{A}$ are
    $$\lambda_1 = -2+i, \quad \lambda_2=-2-i, \qquad \mathbf{K}_1 = \begin{pmatrix} -2-i \\ 5 \end{pmatrix}, \quad \mathbf{K}_2 = \begin{pmatrix} -2+i \\ 5 \end{pmatrix}$$
Then use the technique in example 6 in section 8.2.3 to write out the general solution as a linear combination of real solutions, and then use the initial values.  Confirm that $x(t)$ is the same as from parts A and/or B, and thereby compute $x(2)$.
\item Problem \eqref{homo} is a \emph{damped mass-spring}, as studied in \S5.1: $m=1$, $\beta=4$, and $k=5$.  Is it overdamped, critically damped, or underdamped?
\item Use the \S4.4 \emph{undetermined coefficients} method to solve problem \eqref{nonhomo}.  Compute $x(2)$.
\item Use Chapter 7 \emph{Laplace transform} methods to solve problem \eqref{nonhomo}.  Compute $x(2)$.
\item Use the black-box numerical solver \href{https://www.mathworks.com/help/matlab/ref/ode45.html}{\texttt{ode45}} to solve problem \eqref{nonhomo}.  Approximate $x(2)$.  How accurate is the approximation?
% >> f = @(t,z) [z(2); -5*z(1)-4*z(2)+5*sin(t)];
% >> [tt,zz] = ode45(f,[0,2],[0;10]);
% >> zz(end,1)
% ans =  1.0006
\end{enumerate}
\end{document}
